\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://cmitropoulos.github.io/}{\Large Christos Mitropoulos}} & Email : \href{mailto:chris.mitropoulos@gmail.com}{chris.mitropoulos@gmail.com}\\
   & Mobile : +1-732-895-3357 \\
\end{tabular*}

%-----------OBJECTIVE-----------------
\section{Summary}
Experienced Data Scientist with strong Data Engineering skills that has mainly worked in the invalid traffic and fraud detection space. Interested in full stack roles and solving problems end-to-end, from research to deployment and performance monitoring. 

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Oracle Advertising - MOAT}{New York, NY}
      {Senior Data Scientist - Data Engineer}{Jun. 2019 -- present}
      \begin{itemize}
      		\item Performing exploratory data analysis on ad measurement data for desktop, mobile and connected TV devices.
      		\item Designing, implementing and automating data pipelines.
      		\item Designing, implementing and automating machine learning pipelines.
      		\item{Tools: } {Python, scikit-learn, pandas, spark, pymc, SQL, linux, Airflow, Kubernetes, Argo Workflows, Grafana, Prometheus} 
      		\item{Areas: } {Time-series analysis, anomaly detection, unsupervised learning, clustering, bayesian statistics, NLP} 
      \end{itemize}
  	 \resumeSubheading
      {Perspecta Labs (former Vencore Labs, Applied Communication Sciences)}{Baskin Ridge, NJ}
      {Cyber Security Research Intern}{Jun. 2018 -- Aug. 2018}
      	\begin{itemize}      	
  			\item Developing botnets of the Fast Flux family, on top of the CyberVAN tesbed.
  			\item Evaluating the performance of the botnets using intrusion detection systems and machine learning based techniques.
  			\item{Tools: }{C++, Winsock, GoLang, Python, Linux and Windows operating systems.}
      	\end{itemize}
	\resumeSubheading
	   {Rutgers, The State University of New Jersey}{New Brunswick, NJ}
       {Research Assistant - HCI \& Security Engineering Lab - Advisor: Prof. Janne Lindqvist}{Sep. 2016 -- May 2019}
	 \resumeSubheading
      {Rutgers, The State University of New Jersey}{New Brunswick, NJ}
      {Lead Teaching Assistant - Computer Architecture Lab}{Sep. 2016 -- May 2019}
      	\begin{itemize}      	
  			\item Teaching Assembly MIPS  to approximately 80 students. 
  			\item Preparing and grading lab assignments.
      	\end{itemize}
	\resumeSubheading
      {Rutgers, The State University of New Jersey}{New Brunswick, NJ}
      {Research Internship}{Jun. 2014 -- Sep. 2014}
      	\begin{itemize}      	
      		\item{Research Areas: }{Pattern Recognition, Machine Learning, Security and Privacy, Human Computer Interaction}
      	\end{itemize}
     \resumeSubheading
      {Digi4sites.com}{Athens, Greece}
      {Software Engineer}{Jun. 2012-- Sep. 2014}
      	\begin{itemize}      	
      		\item{Responsibilities: }{Developing custom websites using HTML, CSS, jQuery, MySQL; Server administration using Amazon Web Services (AWS) tools.}   
        \end{itemize}     		
  \resumeSubHeadingListEnd

%Interaction, Security Engineering
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rutgers, The State University of New Jersey, HCI \& Security Engineering Lab }{New Brunswick, NJ}
      {Masters in Electrical and Computer Engineering ; Advisor: Prof Janne Lindqvist; GPA: 3.9}{Sep. 2016 -- May 2019}
      	\resumeItemListStart
        	\resumeItem{Courses}{Massive Data Mining and Learning, Parallel and Distributed Computing, Software Engineering, Regression Analysis, Security Engineering, Operating Systems}
        	\resumeItem{Online courses}{Neural Networks and Deep Learning}
        \resumeItemListEnd
    \resumeSubheading
      {National Technical University of Athens (NTUA)}{Athens, Greece}
      {Masters of Engineering in Electrical and Computer Engineering;  GPA 3.6}{Sep. 2010 -- Sep. 2015}
      \resumeItemListStart
        \resumeItem{Thesis}{Created an android based \textbf{Gesture Authentication System} using Machine Learning Models, Hidden Markov Models; Grade                10/10}
          \resumeItem{Courses}{Artificial Intelligence, Databases and Information Systems Engineering, Algorithms and Data Structures, Programming Languages, Computer  - Communication - Mobile Networks}
        \resumeItemListEnd
  \resumeSubHeadingListEnd




%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
   
  \resumeItemListStart
        	\resumeItem{Languages}{Java, Python, C/C++, MATLAB, Javascript,  SQL}
        	\resumeItem{Frameworks/Libraries}{Scikit Learn, Pandas, Hadoop, SQL, AirFlow, Kubernetes, Argo, pthreads, ISPC, Django, }
        	\resumeItem{OS}{Linux, Windows}
    \resumeItemListEnd
%-----------PROJECTS-----------------
\section{Research Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Machine Learning and Social Protocols for Enhancing Spectrum Access}{}
      {Advisor: Prof. Janne Lindqvist}{Sep. 2016 -- Mar 2019}
      		\begin{itemize}
      			\item Designed experiments to measure participants' behavior under lossy networks.
      			\item Designed experiments to get objective video quality assessment of videos streamed under lossy networks.
      		\end{itemize}
  \resumeSubheading
      {Video Guessing Attacks}{}
      {Advisor: Prof. Janne Lindqvist}{Mar. 2018 -- Mar 2019}
      		\begin{itemize}
      			\item Perform PIN guessing attacks based on video with no view of the victim's screen.
      		\end{itemize}   
 \resumeSubheading
      {Human Behavior Prediction}{}
      {Advisor: Prof. Janne Lindqvist}{Sep. 2016 -- Mar 2019}
      		\begin{itemize}
      			\item Create predictive models of human behavior based on collected data.
      			\item Built a web-based tool to facilitate data collection.
      		\end{itemize}  
      		      		
	
  \resumeSubheading
      {Analyze System Administrators' Vulnerability-handling Behavior}{}
      {Advisor: Prof. Janne Lindqvist}{Oct. 2017 -- Dec. 2017}
      		\begin{itemize}
      			\item Mined data from IPv4 network scanners and disclosed vulnerabilities datasets.
      			\item Applied exploratory data analysis methods and created models with predictive power.
      		\end{itemize}  
\resumeSubheading
      {Novel Video Quality metric for Long Videos}{}
      {Advisor: Prof. Janne Lindqvist}{Sep. 2017 -- Dec. 2017}
      		\begin{itemize}
      			\item Developed a novel video quality metric for longer videos, taking into account video freeze events and frame distortions.
      		\end{itemize}  
      		 
\resumeSubheading
      {Social Protocols for Enhancing Network Connectivity Sharing}{}
      {Advisor: Prof. Janne Lindqvist}{Sep. 2017 -- Dec. 2017}
      		\begin{itemize}
      			\item Designed experiments to measure participants network connectivity sharing choice based on nudges.
      			\item Built a web-based tool to facilitate data collection.
      		\end{itemize}  


      		 
      	         	   
      		
\resumeSubHeadingListEnd	

%------------course projects-----
\section{Course Projects}
      	\resumeItemListStart
      	\resumeItem{Massive Data Minining and Learning}{TheNextHit: Predicting movie success and building Content and Collaborative Filtering recommendation system.}
      	\resumeItem{Parallel Computing Project}{Wrote CUDA C/C$++$ code for multi-core CPU architectures and heterogeneous CPU-GPU system applications}
      	 \resumeItem{User Authentication System}{Developed an User authentication system running on Android smart-phones. User-generated gestures are used for identifying the users. Hidden Markov Models were used for modeling the gestures}
        \resumeItem{Restaurant Automation System}{Developed an automation system using the Django Python Framework and the MVC design architecture}
      		\resumeItem{Hotel Management Information System}{Developed a Hotel Management System using Dynamic Web Technologies; PHP, html, css, javascript, MySQL} 		
      	\resumeItemListEnd
%


%---------------Honors ans Awards-------
\section{Honors and Awards}
 \resumeItemListStart
 	\resumeItem{2018}{ Winner of the Rutgers State University TA/GA Development Fund}
	\resumeItem{2017}{ Winner of the Gerondelis Foundation Grant}
 \resumeItemListEnd
%---------------Academic service-------
\section{Academic Service}
 \resumeItemListStart
\resumeItem{SOUPS 2018}{External Reviewer} 
\resumeItem{WWW 2018}{External Reviewer}
\resumeItem{SOUPS 2017}{External Reviewer} 
\resumeItem{IMWUT 2017}{External Reviewer}
 \resumeItemListEnd


%----------------Papers---------
\section{Papers}
\begin{itemize}
	\item Xianyi Gao, Yulong Yang, Can Liu, \textbf{Christos Mitropoulos}, Oulasvirta Antti, Janne Lindqvist. "Forgetting of Passwords: Ecological Theory and Data",USENIX Security '18\\
\end{itemize}

%\section{Papers currently under submission}
%\begin{itemize}
%	\item Meghan McLean, \textbf{Christos Mitropoulos}, Janne Lindqvist. "Tragedy of the Common Hotspot: Social Protocols for Enhancing Network %Connectivity Sharing", CSCW '18
%\end{itemize}
 




%-------------------------------------------
\end{document}
